Mixture Modeling Paper Results

### 2017-03-22 PaperEx170308.Rmd
Add option to change title

#-----------------------------------------------
#[IC4]  rawuncertgraph
#-----------------------------------------------
#Displays the overall uncertainty function (which is 1-max(probability of membership to component i)) with the possible cut-points overlaid. Note: Sometimes the cutpoint does not line up exactly with a peak in the uncertainty function, which looks like a flaw, but is not. In a two component setting, the cutpoint will always occur at the peak of the uncertainty but this is not always the case when there are more than two components.
rawuncertgraph<-function(modelpickobj,xlab="X Value",xlim=c(NA,NA),suppresslegend=F,setcolor=c(
  "green4",          #1
  "turquoise3",      #2
  "royalblue2",      #3
  "darkorchid2",     #4
  "firebrick3",      #5
  "darkorange2",     #6
  "white",           #7
  "grey",            #8
  "black"            #9
)){

  grobj<-list()
  if (is.na(xlim[1])==T | is.na(xlim[2])==T) {   
    grobj$minval<-(1/10)*trunc(10*min(modelpickobj$datawithids$data)) 
    grobj$maxval<-max(modelpickobj$datawithids$data)
  } else {
    grobj$minval<-xlim[1]
    grobj$maxval<-xlim[2]
  }

  plot(modelpickobj$v, modelpickobj$mcluncert, main=paste("Uncertainty Plot with Possible Cutpoints for", modelpickobj$desc$dist, "with", modelpickobj$desc$ncomp, "components", sep = " "), type="l", ylim=c(0,1), xlim=c(grobj$minval,grobj$maxval), xlab=xlab, ylab="Uncertainty")

@@

#-----------------------------------------------
#[IC5]  rawdistgraph
#-----------------------------------------------
#Displays the distributions of all the components for the chosen combination of distribution and number of components. 
rawdistgraph<-function(modelpickobj,xlim=c(NA,NA),xlab="Optical Density",setbreaks=100,suppresslegend=F,setcolor=c(
  "green4",          #1
  "turquoise3",      #2
  "royalblue2",      #3
  "darkorchid2",     #4
  "firebrick3",      #5
  "darkorange2",     #6
  "white",           #7
  "grey",            #8
  "black"            #9
)){
  #Parameter specification
  ncomp=modelpickobj$desc$ncomp
  grobj<-vector("list")
  grobj$gpar<-vector("list")
  data<-modelpickobj$datawithids$data
  color<-setcolor

@@

@@

  hist(data, freq=F, breaks=setbreaks, xlab=xlab, ylab="Density", main=paste("Distribution of", ncomp, modelpickobj$desc$dist,"Components", sep = " "), border="grey", ylim=grobj$ylim, xlim=grobj$xlim)
  for (i in 1:ncomp) {
    lines(grobj$t, grobj$gt[[i]], lwd=2, col=grobj$colors[i])
  }
  lines(grobj$t, grobj$gt[[length(grobj$gt)]], lwd=2, col=grobj$colors[length(grobj$colors)], lty=2)
  legtxt<-vector("character", ncomp+1)
  colors<-vector("character", ncomp+1)
  for (i in 1:ncomp){
    legtxt[i]<-paste("Distribution of Component ", i, sep="")
    colors[i]<-grobj$colors[i]
  }  
  legtxt[ncomp+1]<-"Overall Distribution"
  colors[ncomp+1]<-grobj$colors[length(grobj$colors)]
  linetype<-c(1)[rep(c(1), times=ncomp)]
  if (suppresslegend==F) {
    legend("topright", col=colors, lwd=2, legend=legtxt, xjust=1, seg.len=3, title="Distributions", lty=c(linetype,2))
  }

@@

rawhistcuts<-function(modelpickobj,xlab="Optical Density",xlim=c(NA,NA),setbreaks=250,suppresslegend=F,setcolor=c(
  "green4",          #1
  "turquoise3",      #2
  "royalblue2",      #3
  "darkorchid2",     #4
  "firebrick3",      #5
  "darkorange2",     #6
  "white",           #7
  "grey",            #8
  "black"            #9
)){
  data<-modelpickobj$datawithids$data
  grobj<-list()

@@

  ncomp<-modelpickobj$desc$ncomp
  cuts <- cut(hist$breaks, c(-Inf,modelpickobj$cutpoint,Inf))

@@

  cuts<-as.numeric(cuts)
  colors<-vector("character", length(cuts))
  for (i in 1:max(cuts)){
    for (j in 1:length(cuts)){
      if (cuts[j]==i) {
        colors[j]<-col[i]
      }
    }
  }
  plot(hist, col=colors, xlab=xlab, ylab="Density", main=paste("Classification by", modelpickobj$desc$dist, "with", ncomp, "components", sep = " "), freq=F, lty="blank")

@@

#-----------------------------------------------
#[IC8] cutuncertgraph
#-----------------------------------------------
#Displays the uncertainty function after components have been combined to create positive and negative components with cut-points and bounds of indeterminate range(s) overlaid. Accepts results from both standard and nonstandard cutpoints (from the functions standindet and specindet respectively).
cutuncertgraph<-function(cutobj,xlab="Optical Density",xlim=c(NA,NA),suppresslegend=F,setcolor=c(
  "green4",          #1
  "turquoise3",      #2
  "royalblue2",      #3
  "darkorchid2",     #4
  "firebrick3",      #5
  "darkorange2",     #6
  "white",           #7
  "grey",            #8
  "black"            #9
)){
  color=setcolor
  grobj<-vector("list")

  if (is.na(xlim[1])==T | is.na(xlim[2])==T) {   
    plot(cutobj$uncertdf$v, cutobj$uncertdf$uncertainty.v, main=paste("Uncertainty Plot of", cutobj$desc$dist, "with", cutobj$desc$ncomp, "components, cut between distributions", cutobj$desc$cutcomp, "and", (cutobj$desc$cutcomp+1), sep = " "),type="l", ylim=c(0,1), xlab=xlab, ylab="Uncertainty")
  } else {
    grobj$minval<-xlim[1]
    grobj$maxval<-xlim[2]
    plot(cutobj$uncertdf$v, cutobj$uncertdf$uncertainty.v, main=paste("Uncertainty Plot of", cutobj$desc$dist, "with", cutobj$desc$ncomp, "components, cut between distributions", cutobj$desc$cutcomp, "and", (cutobj$desc$cutcomp+1), sep = " "),type="l", ylim=c(0,1), xlab=xlab, ylab="Uncertainty", xlim=c(grobj$minval,grobj$maxval))
  }

@@

#-----------------------------------------------
#[IC9]  cutdistgraph
#-----------------------------------------------
#Displays the distributions of the positive and negative components with cut-points and bounds of indeterminate range(s) overlaid. Accepts results from both standard and nonstandard cutpoints (from the functions standindet and specindet respectively). 
cutdistgraph<-function(cutobj,xlim=c(NA,NA),xlab="Optical Density",setbreaks=100,suppresslegend=F,setcolor=c(
  "green4",          #1
  "turquoise3",      #2
  "royalblue2",      #3
  "darkorchid2",     #4
  "firebrick3",      #5
  "darkorange2",     #6
  "white",           #7
  "grey",            #8
  "black"            #9
)){
  #Parameter specification
  ncomp<-cutobj$desc$ncomp
  cutcomp<-cutobj$desc$cutcomp
  cutobj<-cutobj
  data<-cutobj$datawithids$data
  color<-setcolor

@@

@@

  #Plot Graph
  hist(data, freq=F, breaks=setbreaks, xlab=xlab, ylab="Density", main=paste(cutobj$desc$dist, "with", cutobj$desc$ncomp, "components, cut between distributions", cutobj$desc$cutcomp, "and", (cutobj$desc$cutcomp+1), sep = " "), border=color[8], ylim=grobj$ylim, xlim=grobj$xlim)

  for (i in 1:2) {
    lines(cutobj$uncertdf$v, grobj$gt[[i]], lwd=2, col=grobj$colors[i])
  }
  lines(grobj$t, grobj$gt[[length(grobj$gt)]], lwd=2, col=grobj$colors[length(grobj$colors)], lty=2)
  abline(v =cutobj$cutpoint, untf = T, col=color[6], lwd=1)
  if (cutobj$type=="Standard") {
    abline(v =cutobj$bound80, untf = T, col=color[2], lwd=1)
    abline(v =cutobj$bound90, untf = T, col=color[4], lwd=1)
    if (suppresslegend==F) {
      legtxt<-c("Negative Distribution",
                "Positive Distribution",
                "Overall Distribution",
                paste("Cutpoint=", round(cutobj$cutpoint, 2), sep =""), 
                "Indeterminate Range with", 
                paste("80% Certainty: (", round(cutobj$bound80[1], 2), " , ", round(cutobj$bound80[2], 2), ")", sep =""),
                "Indeterminate Range with", 
                paste("90% Certainty: (", round(cutobj$bound90[1], 2), " , ", round(cutobj$bound90[2], 2), ")", sep ="")
      )
      legend("topright", col=c(color[1], color[5], color[9], color[6], color[2], "white", color[4], "white"), lwd=c(2,2,2,1,1,1,1,1), legend=legtxt, xjust=1, seg.len=3, title="Distributions, Cutpoint, and Boundaries", lty=c(1,1,2,1,1,1,1,1))
    }
  } else if (cutobj$type=="Non.Standard") {
    abline(v =cutobj$bound, untf = T, col=color[3], lwd=1)
    if (suppresslegend==F){
      legtxt<-c("Negative Distribution",
                "Positive Distribution",
                "Overall Distribution",
                paste("Cutpoint=", round(cutobj$cutpoint, 2), sep =""), 
                "Indeterminate Range with", 
                paste((cutobj$desc$uncertlevel*100), "% Certainty: (", round(cutobj$bound[1], 2), " , ", round(cutobj$bound[2], 2), ")", sep ="")
      )
      legend("topright", col=c(color[1], color[5], color[9], color[6], color[3], "white"), lwd=c(2,2,2,1,1,1), legend=legtxt, xjust=1, seg.len=3, title="Distributions, Cutpoint, and Boundaries", lty=c(1,1,2,1,1,1))
    }
  } else {
    abline(v =cutobj$bound80, untf = T, col=color[2], lwd=1)
    abline(v =cutobj$bound90, untf = T, col=color[4], lwd=1)
    abline(v =cutobj$bound, untf = T, col=color[3], lwd=1)
    if (suppresslegend==F){
    legtxt<-c("Negative Distribution",
              "Positive Distribution",
              "Overall Distribution",
              paste("Cutpoint=", round(cutobj$cutpoint, 2), sep =""), 
              "Indeterminate Range with", 
              paste("80% Certainty: (", round(cutobj$bound80[1], 2), " , ", round(cutobj$bound80[2], 2), ")", sep =""),
              "Indeterminate Range with", 
              paste("90% Certainty: (", round(cutobj$bound90[1], 2), " , ", round(cutobj$bound90[2], 2), ")", sep =""),
              "Indeterminate Range with", 
              paste((100*cutobj$desc$certlevel), "% Certainty: (", round(cutobj$bound[1], 2), " , ", round(cutobj$bound[2], 2), ")", sep ="")
      )
    legend("topright", col=c(color[1], color[5], color[9], color[6], color[2], "white", color[4], "white", color[3], "white"), lwd=c(2,2,2,1,1,1,1,1,1,1), legend=legtxt, xjust=1, seg.len=3, title="Distributions, Cutpoint, and Boundaries", lty=c(1,1,2,1,1,1,1,1,1,1))
    }
  }

@@

hist(examp1$data, breaks=100, main="Histogram of Data")
dens1<-density(examp1$data)
plot(dens1, main="Density of Data")

@@

bicgraph(fitobj=fitloopsobject1)

@@

rawuncertgraph(modelpickobject1)
rawdistgraph(modelpickobject1)
rawhistcuts(modelpickobject1)

@@

cutuncertgraph(cutobj = cutoffobject1)
cutdistgraph(cutobj = cutoffobject1)

@@

hist(examp2$data, breaks=100, main="Histogram of Data")
dens2<-density(examp2$data)
plot(dens2, main="Density of Data")

@@

bicgraph(fitobj = fitloopsobject2)

@@

rawuncertgraph(modelpickobj = modelpickobject2)
rawdistgraph(modelpickobj = modelpickobject2)
rawhistcuts(modelpickobj = modelpickobject2)

@@

cutuncertgraph(cutobj = cutoffobject2)
cutdistgraph(cutobj = cutoffobject2)

>>>>

#-----------------------------------------------
#[IC4]  rawuncertgraph
#-----------------------------------------------
#Displays the overall uncertainty function (which is 1-max(probability of membership to component i)) with the possible cut-points overlaid. Note: Sometimes the cutpoint does not line up exactly with a peak in the uncertainty function, which looks like a flaw, but is not. In a two component setting, the cutpoint will always occur at the peak of the uncertainty but this is not always the case when there are more than two components.
rawuncertgraph<-function(modelpickobj,xlab="X Value",xlim=c(NA,NA),suppresslegend=F,title="default",setcolor=c(
  "green4",          #1
  "turquoise3",      #2
  "royalblue2",      #3
  "darkorchid2",     #4
  "firebrick3",      #5
  "darkorange2",     #6
  "white",           #7
  "grey",            #8
  "black"            #9
)){

  if (title!="default"){
    title=title
  } else {
    title=paste("Uncertainty Plot with Possible Cutpoints for", modelpickobj$desc$dist, "with", modelpickobj$desc$ncomp, "components", sep = " ")
  }
  grobj<-list()
  if (is.na(xlim[1])==T | is.na(xlim[2])==T) {   
    grobj$minval<-(1/10)*trunc(10*min(modelpickobj$datawithids$data)) 
    grobj$maxval<-max(modelpickobj$datawithids$data)
  } else {
    grobj$minval<-xlim[1]
    grobj$maxval<-xlim[2]
  }

  plot(modelpickobj$v, modelpickobj$mcluncert, main=title, type="l", ylim=c(0,1), xlim=c(grobj$minval,grobj$maxval), xlab=xlab, ylab="Uncertainty")

@@

#-----------------------------------------------
#[IC5]  rawdistgraph
#-----------------------------------------------
#Displays the distributions of all the components for the chosen combination of distribution and number of components. 
rawdistgraph<-function(modelpickobj,xlim=c(NA,NA),xlab="Optical Density",setbreaks=100,suppresslegend=F,title="default",setcolor=c(
  "green4",          #1
  "turquoise3",      #2
  "royalblue2",      #3
  "darkorchid2",     #4
  "firebrick3",      #5
  "darkorange2",     #6
  "white",           #7
  "grey",            #8
  "black"            #9
)){
  #Parameter specification
  ncomp=modelpickobj$desc$ncomp
  grobj<-vector("list")
  grobj$gpar<-vector("list")
  data<-modelpickobj$datawithids$data
  color<-setcolor

@@

  if (title!="default"){
    title=title
  } else {
    title=paste("Distribution of", ncomp, modelpickobj$desc$dist,"Components", sep = " ")
  }

@@

  hist(data, freq=F, breaks=setbreaks, xlab=xlab, ylab="Density", main=title, border="grey", ylim=grobj$ylim, xlim=grobj$xlim)
  for (i in 1:ncomp) {
    lines(grobj$t, grobj$gt[[i]], lwd=2, col=grobj$colors[i])
  }
  lines(grobj$t, grobj$gt[[length(grobj$gt)]], lwd=2, col=grobj$colors[length(grobj$colors)], lty=2)
  legtxt<-vector("character", ncomp+1)
  colors<-vector("character", ncomp+1)
  for (i in 1:ncomp){
    legtxt[i]<-paste("Distribution of Component ", i, sep="")
    colors[i]<-grobj$colors[i]
  }  
  legtxt[ncomp+1]<-"Overall Distribution"
  colors[ncomp+1]<-grobj$colors[length(grobj$colors)]
  linetype<-c(1)[rep(c(1), times=ncomp)]
  if (suppresslegend==F) {
    legend("topright", col=colors, lwd=2, legend=legtxt, xjust=1, seg.len=3, title="Distributions", lty=c(linetype,2))
  }

@@

rawhistcuts<-function(modelpickobj,xlab="Optical Density",xlim=c(NA,NA),setbreaks=250,suppresslegend=F,title="default",setcolor=c(
  "green4",          #1
  "turquoise3",      #2
  "royalblue2",      #3
  "darkorchid2",     #4
  "firebrick3",      #5
  "darkorange2",     #6
  "white",           #7
  "grey",            #8
  "black"            #9
)){
  data<-modelpickobj$datawithids$data
  grobj<-list()

@@

  ncomp<-modelpickobj$desc$ncomp

  if (title!="default"){
    title=title
  } else {
    title=paste("Classification by", modelpickobj$desc$dist, "with", ncomp, "components", sep = " ")
  }

  cuts <- cut(hist$breaks, c(-Inf,modelpickobj$cutpoint,Inf))

@@

  cuts<-as.numeric(cuts)
  colors<-vector("character", length(cuts))
  for (i in 1:max(cuts)){
    for (j in 1:length(cuts)){
      if (cuts[j]==i) {
        colors[j]<-col[i]
      }
    }
  }
  plot(hist, col=colors, xlab=xlab, ylab="Density", main=title, freq=F, lty="blank")

@@

#-----------------------------------------------
#[IC8] cutuncertgraph
#-----------------------------------------------
#Displays the uncertainty function after components have been combined to create positive and negative components with cut-points and bounds of indeterminate range(s) overlaid. Accepts results from both standard and nonstandard cutpoints (from the functions standindet and specindet respectively).
cutuncertgraph<-function(cutobj, xlab="Optical Density", xlim=c(NA,NA), suppresslegend=F, title="default", setcolor=c(
  "green4",          #1
  "turquoise3",      #2
  "royalblue2",      #3
  "darkorchid2",     #4
  "firebrick3",      #5
  "darkorange2",     #6
  "white",           #7
  "grey",            #8
  "black"            #9
)){
  color=setcolor
  grobj<-vector("list")

  if (title!="default"){
    title=title
  } else {
    title=paste("Uncertainty Plot of", cutobj$desc$dist, "with", cutobj$desc$ncomp, "components, cut between distributions", cutobj$desc$cutcomp, "and", (cutobj$desc$cutcomp+1), sep = " ")
  }

  if (is.na(xlim[1])==T | is.na(xlim[2])==T) {   
    plot(cutobj$uncertdf$v, cutobj$uncertdf$uncertainty.v, main=title, type="l", ylim=c(0,1), xlab=xlab, ylab="Uncertainty")
  } else {
    grobj$minval<-xlim[1]
    grobj$maxval<-xlim[2]
    plot(cutobj$uncertdf$v, cutobj$uncertdf$uncertainty.v, main=title, type="l", ylim=c(0,1), xlab=xlab, ylab="Uncertainty", xlim=c(grobj$minval,grobj$maxval))
  }

@@

#-----------------------------------------------
#[IC9]  cutdistgraph
#-----------------------------------------------
#Displays the distributions of the positive and negative components with cut-points and bounds of indeterminate range(s) overlaid. Accepts results from both standard and nonstandard cutpoints (from the functions standindet and specindet respectively). 
cutdistgraph<-function(cutobj,xlim=c(NA,NA),xlab="Optical Density",setbreaks=100,suppresslegend=F,title="default",setcolor=c(
  "green4",          #1
  "turquoise3",      #2
  "royalblue2",      #3
  "darkorchid2",     #4
  "firebrick3",      #5
  "darkorange2",     #6
  "white",           #7
  "grey",            #8
  "black"            #9
)){
  #Parameter specification
  ncomp<-cutobj$desc$ncomp
  cutcomp<-cutobj$desc$cutcomp
  cutobj<-cutobj
  data<-cutobj$datawithids$data
  color<-setcolor

@@

  if (title!="default"){
    title=title
  } else {
    title=paste(cutobj$desc$dist, "with", cutobj$desc$ncomp, "components, cut between distributions", cutobj$desc$cutcomp, "and", (cutobj$desc$cutcomp+1), sep = " ")
  }

@@

  #Plot Graph
  hist(data, freq=F, breaks=setbreaks, xlab=xlab, ylab="Density", main=title, border=color[8], ylim=grobj$ylim, xlim=grobj$xlim)

  for (i in 1:2) {
    lines(cutobj$uncertdf$v, grobj$gt[[i]], lwd=2, col=grobj$colors[i])
  }
  lines(grobj$t, grobj$gt[[length(grobj$gt)]], lwd=2, col=grobj$colors[length(grobj$colors)], lty=2)
  abline(v =cutobj$cutpoint, untf = T, col=color[6], lwd=1)
  if (cutobj$type=="Standard") {
    abline(v =cutobj$bound80, untf = T, col=color[2], lwd=1)
    abline(v =cutobj$bound90, untf = T, col=color[4], lwd=1)
    if (suppresslegend==F) {
      legtxt<-c("Negative Distribution",
                "Positive Distribution",
                "Overall Distribution",
                paste("Cutpoint=", round(cutobj$cutpoint, 2), sep =""), 
                "Indeterminate Range with", 
                paste("80% Certainty: (", round(cutobj$bound80[1], 2), " , ", round(cutobj$bound80[2], 2), ")", sep =""),
                "Indeterminate Range with", 
                paste("90% Certainty: (", round(cutobj$bound90[1], 2), " , ", round(cutobj$bound90[2], 2), ")", sep ="")
      )
      legend("topright", col=c(color[1], color[5], color[9], color[6], color[2], "white", color[4], "white"), lwd=c(2,2,2,1,1,1,1,1), legend=legtxt, xjust=1, seg.len=3, title="Distributions, Cutpoint, and Boundaries", lty=c(1,1,2,1,1,1,1,1))
    }
  } else if (cutobj$type=="Non.Standard") {
    abline(v =cutobj$bound, untf = T, col=color[3], lwd=1)
    if (suppresslegend==F){
      legtxt<-c("Negative Distribution",
                "Positive Distribution",
                "Overall Distribution",
                paste("Cutpoint=", round(cutobj$cutpoint, 2), sep =""), 
                "Indeterminate Range with", 
                paste((cutobj$desc$certlevel*100), "% Certainty: (", round(cutobj$bound[1], 2), " , ", round(cutobj$bound[2], 2), ")", sep ="")
      )
      legend("topright", col=c(color[1], color[5], color[9], color[6], color[3], "white"), lwd=c(2,2,2,1,1,1), legend=legtxt, xjust=1, seg.len=3, title="Distributions, Cutpoint, and Boundaries", lty=c(1,1,2,1,1,1))
    }
  } else {
    abline(v =cutobj$bound80, untf = T, col=color[2], lwd=1)
    abline(v =cutobj$bound90, untf = T, col=color[4], lwd=1)
    abline(v =cutobj$bound, untf = T, col=color[3], lwd=1)
    if (suppresslegend==F){
    legtxt<-c("Negative Distribution",
              "Positive Distribution",
              "Overall Distribution",
              paste("Cutpoint=", round(cutobj$cutpoint, 2), sep =""), 
              "Indeterminate Range with", 
              paste("80% Certainty: (", round(cutobj$bound80[1], 2), " , ", round(cutobj$bound80[2], 2), ")", sep =""),
              "Indeterminate Range with", 
              paste("90% Certainty: (", round(cutobj$bound90[1], 2), " , ", round(cutobj$bound90[2], 2), ")", sep =""),
              "Indeterminate Range with", 
              paste((100*cutobj$desc$certlevel), "% Certainty: (", round(cutobj$bound[1], 2), " , ", round(cutobj$bound[2], 2), ")", sep ="")
      )
    legend("topright", col=c(color[1], color[5], color[9], color[6], color[2], "white", color[4], "white", color[3], "white"), lwd=c(2,2,2,1,1,1,1,1,1,1), legend=legtxt, xjust=1, seg.len=3, title="Distributions, Cutpoint, and Boundaries", lty=c(1,1,2,1,1,1,1,1,1,1))
    }
  }

@@

hist(examp1$data, breaks=100, main="")
dens1<-density(examp1$data)
plot(dens1, main="")

@@

bicgraph(fitobj=fitloopsobject1, title="")

@@

rawuncertgraph(modelpickobject1, title="")
rawdistgraph(modelpickobject1, title="")
rawhistcuts(modelpickobject1, title="")

@@

cutuncertgraph(cutobj = cutoffobject1, title="")
cutdistgraph(cutobj = cutoffobject1, title="")

@@

hist(examp2$data, breaks=100, main="")
dens2<-density(examp2$data)
plot(dens2, main="")

@@

bicgraph(fitobj = fitloopsobject2, title="")

@@

rawuncertgraph(modelpickobj = modelpickobject2, title="")
rawdistgraph(modelpickobj = modelpickobject2, title="")
rawhistcuts(modelpickobj = modelpickobject2, title="")

@@

cutuncertgraph(cutobj = cutoffobject2, title="")
cutdistgraph(cutobj = cutoffobject2, title="")
